Biologically-Constrained 3D Agglomeration for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/3_evaluation.tex
pass on exp and result

\subsubsection{Kasthuri}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
This dataset is $5342 \times 3618 \times 338$ voxels in size. 
The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
We evaluate our methods using the left cylinder of this 3-cylinder dataset. 
We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. 
We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $1335 \times 1809 \times 338$ voxels.

\subsubsection{FlyEM}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The mushroom body in this species is the primary site of associative learning. 
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $999 \times 999 \times 999$ voxels.

\subsubsection{Fib-25}
The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}. This sample is imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$. 
There is currently a reconstruction challenge based on this sample.

\subsection{Pixel-Based Segmentations}
\label{sec:neuroproof}

%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
We first train a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and apply the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.

\subsection{Graph Pruning Parameters}

The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
We explore these thresholds in greater detail in the supplemental material.

In our implementation we use nanometers for these thresholds and not voxels. 
Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
Although the voxels vary between different datasets, the physical space remains constant.

\subsection{Classifier Training}
\label{sec:network-parameters}

We use half of the Kasthuri and FlyEM datasets\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.} for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates.

@@

\subsubsection{Training Augmentation.}

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

\subsection{Error Metrics}
\label{sec:variation-of-information}

We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. 
Since we are measuring the entropy between two clusterings, lower VI scores are better.

>>>>

%\subsubsection{Kasthuri}
\noindent\textbf{Kasthuri}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
This dataset is $5342 \times 3618 \times 338$ voxels in size. 
The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
We evaluate our methods using the left cylinder of this 3-cylinder dataset. 
We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. 
We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $1335 \times 1809 \times 338$ voxels.

%\subsubsection{FlyEM}
\noindent\textbf{FlyEM}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The mushroom body in this species is the primary site of associative learning. 
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $999 \times 999 \times 999$ voxels.

%\subsubsection{Fib-25}
\noindent\textbf{Fib-25}
The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}. This sample is imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$. 
There is currently a reconstruction challenge based on this sample.

\subsection{Method Configuration}
\noindent\textbf{Initial Segmentation}
%\label{sec:neuroproof}
%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
We first train a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and apply the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.

\noindent\textbf{Graph Generation}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
We explore these thresholds in greater detail in the supplemental material.
During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
% Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
% Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
% Although the voxels vary between different datasets, the physical space remains constant.

\noindent\textbf{Edge Weight Learning}
\label{sec:network-parameters}
We use half of the Kasthuri and FlyEM datasets\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.} for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates.

@@

%\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

\noindent\textbf{Graph Partition} \TODO{parameters?}

\subsection{Error Metrics}
\label{sec:variation-of-information}
We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. 
Since we are measuring the entropy between two clusterings, lower VI scores are better.

### 2018-03-14 papers/eccv2018/4_results.tex
eccv: fixed figures to be horizontally aligned
pass on exp and result

\subsection{Variation of Information Results}

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green). 
We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
The results from our method are shown in red for varying the $\beta$ parameter. 
We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

@@

\subsection{Graph Pruning Results}

Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
However, there are some adjacent over-segmented labels which are not considered. 
Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
We present additional analysis of the skeletonization parameters in the supplemental material.

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
	\label{fig:skeleton-results}
\end{figure}

\subsection{CNN Classification Results}

\subsubsection{Inference Augmentation}

Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

@@

\subsubsection{Generalization to Other Datasets}

Our neural network does not take as input the images or affinities to allow us to transfer network weights from one dataset to the next.
Table~\TODO{X} shows the result when training on the FlyEM data and inferring on the Kasthuri data and vice versa.
The classification results are reasonable despite the fact that the datasets vary in resolution and even animal type.

\subsection{Graph Optimization Results}

The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and ``lifted'' multicut formulations.
These results correspond to $\beta = 0.5$ (Sec.~\ref{sec:edge-weights}). 
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
The ``lifted'' variant further accentuates this trend of increasing precision and accuracy at the expense of recall. 
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.

@@

\subsection{Computational Performance}

\subsubsection{System} All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. All code is written in Python and will be freely available upon paper decision. We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.

>>>>

\subsection{Connectomics Benchmark}
In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green). 
We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
The results from our method are shown in red for varying the $\beta$ parameter. 
We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

@@

\subsection{Empirical Ablation Studies}
Below, we analyze various design choiceswe for each step of our pipeline.

\noindent\textbf{Graph Generation.}
Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
However, there are some adjacent over-segmented labels which are not considered. 
Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
We present additional analysis of the skeletonization parameters in the supplemental material.

@@

\begin{figure}[t!]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}	
		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
	\end{minipage}
	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples shows pairs of segments that belong to the same neuron but are not adjacent in the input segmentation.}
	\label{fig:skeleton-results}
\end{figure}

%\subsection{CNN Classification Results}
\noindent\textbf{Edge Weight Learning}
We first evaluate the effectiveness of inference augmentation.
%\subsubsection{Inference Augmentation}
%\noindent\textbf{Inference Augmentation.}
Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

@@

%\subsubsection{Generalization to Other Datasets}
%\noindent\textbf{Generalization to Other Datasets.}
We also evaluate the generalization to other datasets.
Our neural network does not take as input the images or affinities to allow us to transfer network weights from one dataset to the next.
Table~\TODO{X} shows the result when training on the FlyEM data and inferring on the Kasthuri data and vice versa.
The classification results are reasonable despite the fact that the datasets vary in resolution and even animal type.

%\subsection{Graph Optimization Results}
\noindent\textbf{Graph Partition}
The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and ``lifted'' multicut formulations.
These results correspond to $\beta = 0.5$ (Sec.~\ref{sec:edge-weights}). 
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
The ``lifted'' variant further accentuates this trend of increasing precision and accuracy at the expense of recall. 
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.

@@

\subsection{Computational Performance}
%\subsubsection{System} 
\noindent\textbf{System}
All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. All code is written in Python and will be freely available upon paper decision. We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.

### 2018-03-14 papers/eccv2018/paper.tex
pass on exp and result

\begin{abstract}
% maybe better to cut to the point
%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
%An agglomerative segmentation algorithm merges initial pair of clusters.
Current state-of-the-art connectome reconstruction pipelines have three major steps: affinity prediction from raw voxels, initial segmentation with watershed transform and refined segmentation with agglomeration.
%In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)
For the agglomeration, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.

>>>>

\begin{abstract}
% maybe better to cut to the point
%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
%An agglomerative segmentation algorithm merges initial pair of clusters.
Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation with agglomeration.
%In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)
For the agglomeration, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
